### 2019-09-16 2019_neurips_vigil/model.tex

\begin{figure}[!b]
\begin{minipage}{0.43\textwidth}
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
\end{minipage}\hfill
\begin{minipage}{0.55\textwidth}
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
\end{minipage}\hfill
\caption{General architecture of SAMNet (left) and a single reasoning step in SAMCell (right)}
\label{fig:samnet}
\end{figure}

\begin{figure}[!t]
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
	\caption{General architecture of SAMNet}
	\label{fig:samneta}
\end{figure}

\begin{figure}[!b]
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
	\caption{Single reasoning step in SAMCell}
	\label{fig:samneta}
\end{figure}

@@

SAMNet is a recurrent model equipped with an external memory for enabling multi-step reasoning over text and video (\cref{fig:samnet}).
The memory is used to store relevant objects representing contextual information about words in text and feature vectors in video frames. The memory 
can be accessed through either content-addressing, via dot-product attention, or location-based addressing. 
Coupled with gating mechanisms to be described later, this enables correct objects to be retrieved 
in order to perform spatio-temporal reasoning on frames and text. Each address of the memory stores
a $d$-dimensional vector, where $d$ is a global parameter.
SAMNet is end-to-end differentiable including its memory update procedures. 
%A notable feature of this design is that the number of addresses $N$ can be set to different values during training and 
%testing to fit the characteristics of data.

The core of SAMNet is a recurrent cell called SAMCell (\cref{fig:samnet}). 
By aligning together a new series of $k$ SAMCells per frame, the network can perform $k$ 
reasoning steps over each frame; the only flow of information between frames is through the external memory. 
For $t=1,2, \dots, k$, SAMCell maintains the following information as part of its recurrent state:
(a) $c_t \in \Reals^d$, the control state used to drive the reasoning over objects in the frame and memory; and
(b) $so_t  \in \Reals^d$, the summary visual object representing the relevant object for step $t$.
Let $M_t \in  \Reals^{N \times d}$ denote the external memory with $N$ slots at the end of step $t$.
Let $\whead_t \in  \Reals^N$ denote an attention vector over the memory locations;
in a trained model, $\whead_t$ points to the location of first empty slot in memory for adding new objects.

>>>>

%\begin{figure}[!b]
%\begin{minipage}{0.43\textwidth}
%	\centering
%	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
%\end{minipage}\hfill
%\begin{minipage}{0.55\textwidth}
%	\centering
%	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
%\end{minipage}\hfill
%\caption{General architecture of SAMNet (left) and a single reasoning step in SAMCell (right)}
%\label{fig:samnet}
%\end{figure}

@@

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
	\caption{General architecture of SAMNet}
	\label{fig:samnet}
\end{figure}

SAMNet is an end-to-end differentiable recurrent model equipped with an external memory for enabling multi-step reasoning over text and video (\cref{fig:samnet}).
The memory is used to store relevant objects representing contextual information about words in text and visual objects in video frames. 
Each address of the memory stores a $d$-dimensional vector, where $d$ is a global parameter.
The memory  can be accessed through either content-addressing, via dot-product attention, or location-based addressing. 
Coupled with gating mechanisms to be described later, this enables correct objects to be retrieved 
in order to perform spatio-temporal reasoning on frames and text. 
%A notable feature of this design is that the number of addresses $N$ can be set to different values during training and 
%testing to fit the characteristics of data.

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
	\caption{Single reasoning step in SAMCell}
	\label{fig:samcell}
\end{figure}

The core of SAMNet is a recurrent cell called SAMCell (\cref{fig:samcell}). 
By aligning together a new series of $k$ SAMCells per frame, the network can perform $k$ 
reasoning steps over each frame, with information flowing between frames through the external memory. 
While processing a single frame, for $t=1,2, \dots, k$, SAMCell maintains the following information as part of its recurrent state:
(a) $c_t \in \Reals^d$, the control state used to drive the reasoning over objects in the frame and memory; and
(b) $so_t  \in \Reals^d$, the summary visual object representing the relevant object for step $t$.
Let $M_t \in  \Reals^{N \times d}$ denote the external memory with $N$ slots at the end of step $t$.
Let $\whead_t \in  \Reals^N$ denote an attention vector over the memory locations;
in a trained model, $\whead_t$ points to the location of first empty slot in memory for adding new objects.
